---
title: "Ici-Radio-Canada-Web-Scrape"
output: html_notebook
---

# load the libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(RSelenium)
library(rvest)
```

# build link index, in this case using "coronavirus" as key word
```{r message=FALSE, warning=FALSE}
nums <- 1:500

urls_coronavirus <- paste("https://ici.radio-canada.ca/recherche?pageNumber=", nums, "&q=coronavirus", sep = "")

#test <- "https://ici.radio-canada.ca/recherche?pageNumber=152&q=coronavirus"

driver <- rsDriver(browser = "firefox", port = 4833L)

remote_driver <- driver[["client"]]

liste_temp <- list()

for(u in urls_coronavirus) {
  
  cat(glue::glue("Getting data from {u}"))
  
  remote_driver$navigate(u)
  
  Sys.sleep(1)
  
  html <- remote_driver$getPageSource()[[1]]

  page <- read_html(html)
  
  titre <- page %>%
    html_nodes('.full-width-xs') %>%
    html_nodes('.u-theme-item-wrapper') %>%
    html_nodes('.card-click-overlay') %>%
    html_text(trim = TRUE)
  
  lien <- page %>%
    html_nodes('.full-width-xs') %>%
    html_nodes('.u-theme-item-wrapper') %>%
    html_nodes('.list-card-container') %>%
    html_nodes('a') %>%
    html_attr("href") %>%
    url_absolute(u)
  
  lien <- lien %>%
    as_tibble() %>%
    filter(!str_detect(value, "theme")) %>%
    filter(str_detect(value, "[0-9]+")) %>%
    distinct(value)
  
  date <- page %>%
    html_nodes('.m-published-date-time') %>%
    html_text(trim = TRUE)
  
  mots_cles <- page %>%
    html_nodes('.list-card-container') %>%
    html_node('footer') %>%
    html_text(trim = FALSE)
  
  df <- tibble(
    titre = titre,
    lien_article = lien$value,
    lien_recherche = u,
    date = date,
    mots_cles = mots_cles
  )
  
  liste_temp[[u]] <- df
  
  Sys.sleep(sample(3:10, 1))
  
}
```

# save results in `ici_radio_index`
```{r}
ici_radio_index <- bind_rows(liste_temp)
```

# build link index using "covid" as key word
```{r}
nums <- 1:500

urls_coronavirus <- paste("https://ici.radio-canada.ca/recherche?pageNumber=", nums, "&q=covid", sep = "")

#driver <- rsDriver(browser = "firefox", port = 4833L)

#remote_driver <- driver[["client"]] 

liste_temp2 <- list()

for(u in urls_coronavirus) {
  
  cat(glue::glue("Getting data from {u}"))
  
  remote_driver$navigate(u)
  
  Sys.sleep(1)
  
  html <- remote_driver$getPageSource()[[1]]

  page <- read_html(html)
  
  titre <- page %>%
    html_nodes('.full-width-xs') %>%
    html_nodes('.u-theme-item-wrapper') %>%
    html_nodes('.card-click-overlay') %>%
    html_text(trim = TRUE)
  
  lien <- page %>%
    html_nodes('.full-width-xs') %>%
    html_nodes('.u-theme-item-wrapper') %>%
    html_nodes('.list-card-container') %>%h
    html_nodes('a') %>%
    html_attr("href") %>%
    url_absolute(u)
  
  lien <- lien %>%
    as_tibble() %>%
    filter(!str_detect(value, "theme")) %>%
    filter(str_detect(value, "[0-9]+")) %>%
    distinct(value)
  
  date <- page %>%
    html_nodes('.m-published-date-time') %>%
    html_text(trim = TRUE)
  
  mots_cles <- page %>%
    html_nodes('.list-card-container') %>%
    html_node('footer') %>%
    html_text(trim = FALSE)
  
  df <- tibble(
    titre = titre,
    lien_article = lien$value,
    lien_recherche = u,
    date = date,
    mots_cles = mots_cles
  )
  
  liste_temp2[[u]] <- df
  
  Sys.sleep(sample(3:10, 1))
  
}
```

# save results in `ici_radio_index2`
```{r}
ici_radio_index2 <- bind_rows(liste_temp2)
```

# merge the two indexes to form `ici_radio_index_joined`, fltering for only unique links
```{r}
ici_radio_index_joined <- ici_radio_index %>%
  bind_rows(ici_radio_index2) %>%
  distinct(lien_article, .keep_all = TRUE)
```

# get information from each link (title, text, author, date)
```{r}
list_temp3 <- list()

for (i in ici_radio_index_joined$lien_article) {
  
  cat(glue::glue("Getting {i}"))
  
  try({
      
    page <- read_html(i)
    
    tryCatch({
      titre2 <- page %>% html_node("body") %>% html_node("h1") %>% html_text(trim = TRUE)}, 
      error = {NA})
  
    tryCatch({
      texte <- page %>% html_nodes(".document-simple-redactional-container .e-p") %>% html_text(trim = TRUE) %>% str_c(collapse = " ")},
      error = {NA})
  
    tryCatch({
      auteur <- page %>% html_node(".signature-avatar-first-name") %>% html_text(trim = TRUE)}, 
      error = {NA})

    tryCatch({
      date2 <- page %>% html_node(".m-published-date-time") %>% html_text(trim = TRUE)}, 
      error = {NA})
  
    df <- tibble(
      titre2 = titre2,
      texte = texte,
      auteur = auteur,
      date2 = date2,
      lien_article = i
      )
    
    list_temp3[[i]] <- df
    
    })
  
  Sys.sleep(sample(3:10, 1))
  
  }
```

# save results in `ici_radio_articles`
```{r}
ici_radio_articles <- list_temp3 %>% bind_rows()
```

# save `ici_radio_index_joined` and `ici_radio_articles` as csv files
```{r}
write_csv(ici_radio_index_joined, "<PATH/FILENAME.csv>")

write_csv(ici_radio_articles, "<PATH/FILENAME.csv>")
```
